Convolutional Neural Networks on Graphs\\ with Fast Localized Spectral Filtering

### 2016-10-29 nips2016/nips2016.tex
nips v7: spacing and runtime pdf image

@@

\begin{figure}[ht]
\vspace{0.5cm}
\centering
\includegraphics[width=\textwidth]{images/coarsening_crop}
\caption{\textbf{Example of Graph Coarsening and Pooling.} Let us carry out a max pooling of size 4 (or two poolings of size 2) on a signal $x \in
\R^8$ living on $\G_0$, the finest graph given as input. Note that it originally
possesses $n_0 = |\V_0| = 8$ vertices, arbitrarily ordered. For a pooling of
size 4, two coarsenings of size 2 are needed: Graclus first gives $\G_1$ of size
$n_1 = |\V_1| = 5$, then $\G_2$ of size $n_2 = |\V_2| = 3$, the coarsest graph.
Sizes are thus set to $n_2 = 3$, $n_1 = 6$, $n_0 = 12$ and fake nodes (in blue)
are added to $\V_1$ (1 node) and $\V_0$ (4 nodes) to pair with the singeltons
(in orange), such that each node has exactly two children.  Nodes in $\V_2$ are
then arbitrarily ordered and nodes in $\V_1$ and $\V_0$ are ordered
consequently.  At that point the arrangement of vertices in $\V_0$ permits a
regular 1D pooling on $x \in \R^{12}$ such that $z = [\max(x_0,x_1),
\max(x_4,x_5,x_6), \max(x_8,x_9,x_{10})] \in \R^3$, where the signal components
$x_2,x_3,x_7,x_{11}$ are set to a neutral value.}
\label{fig:pooling}
\end{figure}

@@

\begin{table*}[h!] \centering
\vspace{0.5cm}
\begin{tabular}{lc} \toprule
Model & Accuracy \\
\midrule
Linear SVM & 65.90 \\
Multinomial Naive Bayes & 68.51 \\
%Multinomial logistic regression (softmax) & 66.28 \\
Softmax & 66.28 \\
\addlinespace
FC2500 & 64.64 \\
FC2500-FC500 & 65.76 \\
\addlinespace
GC32 & 68.26 \\
GC32-FC500 & \todo{?} \\
\bottomrule \end{tabular}
\caption{Classification accuracies for the proposed model and a other algorithms
on 20NEWS.} 
\label{tab:20news}
\end{table*}

20NEWS consists of 18,846 (11,314 for training and 7,532 for testing) text
documents associated with 20 classes \cite{art:Joachims9620NEWS}. We extracted
the 10,000 most common words from the 93,953 unique words in this corpus. Each
document is represented using the bag-of-words model, normalized across words.
To test our model, we constructed a 16-NN graph of the word2vec
\cite{pro:MikolovChenCorradoDean13word2vec} embedding of those words, which
produced a graph of \todo{$n = |\V| = $ nodes (10k words and ? fake nodes) and
$|\E| = ?$ edges}.  All CNN models were trained for 20 epochs by the Adam
optimizer \cite{art:KingmaBa14AdamOpt} with a learning rate of 0.1, without regularization nor
dropout. The filter support was set to $K = 5$.

@@

\begin{table*}[h!] \centering
\vspace{0.5cm}
\begin{tabular}{llccc} \toprule
& & \multicolumn{3}{c}{Accuracy} \\
\cmidrule{3-5}
Dataset & Architecture & Non-Param \eqnref{filt_non-param} &
Spline \eqnref{filt_spline} \cite{\bruna} &
Chebyshev \eqnref{filt_cheby} \\
\midrule
MNIST & GC10 & 95.75 & 97.26 & \textbf{97.48} \\
MNIST & GC32-P4-GC64-P4-FC512 & 96.28 & 97.15 & \textbf{98.65} \\
20NEWS & GC32 & \todo{?} & \todo{?} & \todo{?} \\
\bottomrule \end{tabular}
\caption{Comparison of accuracy results for different types of spectral filters.
Spline and Chebyshev filters use \todo{$K=20$}, \todo{$K=5$ for 20NEWS}.} 
\label{tab:filters}
\end{table*}

@@

\begin{table*}[h!] \centering
\vspace{0.5cm}
\begin{tabular}{llccc} \toprule
& & \multicolumn{2}{c}{Time (ms)} & \\
Model & Architecture & CPU & GPU & Speedup \\
\midrule
Classical CNN & C32-P4-C64-P4-FC512 & 210 & 31 & 6.77x \\
Proposed graph CNN & GC32-P4-GC64-P4-FC512 & 200 & 25 & 8.00x \\
\bottomrule \end{tabular}
\caption{Time to process a mini-batch of 100 MNIST images. That is the total
training time divided by the number of gradient steps.} 
\label{tab:speedup}
\end{table*}

\begin{figure}[h!]
\vspace{0.5cm}
\centering
\includegraphics[width=7cm]{images/speed.png}
\caption{Training time over a mini-batch of 100 20NEWS documents w.r.t. $n$, the
number of selected words, for the three considered filters. The architecture is
GC32 with $K=5$ for Spline and Chebyshev.}
\label{fig:runtime}
\end{figure}

@@

\begin{table*}[h!]
\vspace{0.5cm}
\centering
\begin{tabular}{lcc} \toprule
Architecture & 8-NN on 2D Euclidean grid & random \\
\midrule
GC32 & 97.40 & 96.88 \\
GC32-P4-GC64-P4-FC512 & 98.65\todo{99.14} & 95.39 \\
\bottomrule \end{tabular}
\caption{Classification accuracies with different graph constructions on MNIST.} 
\label{tab:mnist_quality}
\end{table*}

@@

\begin{table*}[h!] \centering
\vspace{0.5cm}
\begin{tabular}{ccccc} \toprule
& \multicolumn{2}{c}{word2vec} & & \\
bag-of-words & pre-trained & learned & approximate & random \\
\midrule
67.50 & \todo{66.98} & 68.26 & 67.86 & 67.75 \\
\bottomrule \end{tabular}
\caption{Classification accuracies of GC32 with different graph constructions on 20NEWS.} 
\label{tab4b}
\label{tab:20news_quality}
\end{table*}

>>>>

\setlength{\textfloatsep}{20.0pt plus 2.0pt minus 2.0pt}
\setlength{\floatsep}{20.0pt plus 2.0pt minus 2.0pt}
\setlength{\intextsep}{20.0pt plus 2.0pt minus 2.0pt}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{images/coarsening_crop}
\caption{\textbf{Example of Graph Coarsening and Pooling.} Let us carry out a max pooling of size 4 (or two poolings of size 2) on a signal $x \in
\R^8$ living on $\G_0$, the finest graph given as input. Note that it originally
possesses $n_0 = |\V_0| = 8$ vertices, arbitrarily ordered. For a pooling of
size 4, two coarsenings of size 2 are needed: Graclus first gives $\G_1$ of size
$n_1 = |\V_1| = 5$, then $\G_2$ of size $n_2 = |\V_2| = 3$, the coarsest graph.
Sizes are thus set to $n_2 = 3$, $n_1 = 6$, $n_0 = 12$ and fake nodes (in blue)
are added to $\V_1$ (1 node) and $\V_0$ (4 nodes) to pair with the singeltons
(in orange), such that each node has exactly two children.  Nodes in $\V_2$ are
then arbitrarily ordered and nodes in $\V_1$ and $\V_0$ are ordered
consequently.  At that point the arrangement of vertices in $\V_0$ permits a
regular 1D pooling on $x \in \R^{12}$ such that $z = [\max(x_0,x_1),
\max(x_4,x_5,x_6), \max(x_8,x_9,x_{10})] \in \R^3$, where the signal components
$x_2,x_3,x_7,x_{11}$ are set to a neutral value.}
\label{fig:pooling}
\end{figure}

@@

\begin{table*}[h!] \centering
\begin{tabular}{lcc} \toprule
Model & Accuracy & \todo{Parameters} \\
\midrule
Linear SVM & 65.90 \\
Multinomial Naive Bayes & 68.51 \\
%Multinomial logistic regression (softmax) & 66.28 \\
Softmax & 66.28 & $200\times10^3$ \\
\addlinespace
FC2500 & 64.64 & $\sim25\times10^6$ \\
FC2500-FC500 & 65.76 & $\sim26\times10^6$ \\
\addlinespace
GC32 & 68.26 5\\
GC32-FC500 & \todo{?} \\
\bottomrule \end{tabular}
\caption{Classification accuracies for the proposed model and a other algorithms
on 20NEWS.} 
\label{tab:20news}
\end{table*}

20NEWS consists of 18,846 (11,314 for training and 7,532 for testing) text
documents associated with 20 classes \cite{art:Joachims9620NEWS}. We extracted
the 10,000 most common words from the 93,953 unique words in this corpus. Each
document is represented using the bag-of-words model, normalized across words.
To test our model, we constructed a 16-NN graph of the word2vec
\cite{pro:MikolovChenCorradoDean13word2vec} embedding of those words, which
produced a graph of $n = |\V| = 10,000$ nodes (no fake nodes because we do not
coarsen the graph) and
$|\E| = 132,834$ edges. All CNN models were trained for 20 epochs by the Adam
optimizer \cite{art:KingmaBa14AdamOpt} with a learning rate of 0.1, without regularization nor
dropout. The filter support was set to $K = 5$.

@@

\begin{table*}[h!] \centering
\begin{tabular}{llccc} \toprule
& & \multicolumn{3}{c}{Accuracy} \\
\cmidrule{3-5}
Dataset & Architecture & Non-Param \eqnref{filt_non-param} &
Spline \eqnref{filt_spline} \cite{\bruna} &
Chebyshev \eqnref{filt_cheby} \\
\midrule
MNIST & GC10 & 95.75 & 97.26 & \textbf{97.48} \\
MNIST & GC32-P4-GC64-P4-FC512 & 96.28 & 97.15 & \textbf{98.65} \\
20NEWS & GC32 & \todo{?} & \todo{?} & \todo{?} \\
\bottomrule \end{tabular}
\caption{Comparison of accuracy results for different types of spectral filters.
Spline and Chebyshev filters use \todo{$K=20$}, \todo{$K=5$ for 20NEWS}
parameters.} 
\label{tab:filters}
\end{table*}

@@

\begin{table*}[ht] \centering
\begin{tabular}{llccc} \toprule
& & \multicolumn{2}{c}{Time (ms)} & \\
Model & Architecture & CPU & GPU & Speedup \\
\midrule
Classical CNN & C32-P4-C64-P4-FC512 & 210 & 31 & 6.77x \\
Proposed graph CNN & GC32-P4-GC64-P4-FC512 & 200 & 25 & 8.00x \\
\bottomrule \end{tabular}
\caption{Time to process a mini-batch of $S=100$ MNIST images. That is the total
training time divided by the number of gradient steps.} 
\label{tab:speedup}
\end{table*}

\begin{figure}[ht]
\centering
\vspace{-20pt}
\includegraphics[width=\textwidth]{images/runtime_crop}
\caption{Training time over a mini-batch of $S=100$ 20NEWS documents w.r.t. $n$, the
number of selected words, for the three considered filters. The architecture is
GC32 with $K=5$ for Spline and Chebyshev.}
\label{fig:runtime}
\end{figure}

@@

\begin{table*}[h!]
\centering
\begin{tabular}{lcc} \toprule
Architecture & 8-NN on 2D Euclidean grid & random \\
\midrule
GC32 & 97.40 & 96.88 \\
GC32-P4-GC64-P4-FC512 & 98.65\todo{99.14} & 95.39 \\
\bottomrule \end{tabular}
\caption{Classification accuracies with different graph constructions on MNIST.} 
\label{tab:mnist_quality}
\end{table*}

@@

\begin{table*}[h!] \centering
\begin{tabular}{ccccc} \toprule
& \multicolumn{2}{c}{word2vec} & & \\
bag-of-words & pre-trained & learned & approximate & random \\
\midrule
67.50 & \todo{66.98} & 68.26 & 67.86 & 67.75 \\
\bottomrule \end{tabular}
\caption{Classification accuracies of GC32 with different graph constructions on 20NEWS.} 
\label{tab4b}
\label{tab:20news_quality}
\end{table*}
